---
title: "Exercise Set 2"
author: "Cora Ferguson"
date: "1/28/2023"
output: html_document
---

# Exercise Set 2 Overview
## Question 0
The goal of exercise set 2 is to practice some of the things that we have recently discussed in class. The first thing that I will do is enter in the code that is necessary to import data and play around with it.

```{r}
# clear the environment window
rm(list = ls())

# import the libraries that we will be using
library(readr)
library(dplyr)
library(here)
library(ggplot2)
library(knitr)
```
## Question 1
a. The first task is to use functions from the `readr` package to import the data.

```{r}
# import the data
coasters <- read_csv(here("data", "rollercoasters.csv" ))
```
b. Now that the data is in, the next task is to construct a 95% confidence interval for the average duration of a roller coaster.  To do this, I will use the `t.test()` function.

```{r}
# construct a 95% confidence interval
t.test(coasters$Duration)
```
c. Now we are going to take a look at the speed variable which describes the maximum speed of the roller coaster.  We want to determine whether the mean max speed of a roller coaster is significantly different from 55 mph.  To do this, we will perform a t test because we are looking at the difference between two means.

```{r}
# perform a t test on speed comparing the averages from the data to the defined average of 55 mph
t.test(coasters$Speed, mu = 55)
```
Based on this t-test, there is evidence that supports the hypothesis stating that the mean max speed of roller coasters is not 55 mph.

d. Now we will take a look at the data using the `dplyr` package.

```{r}
# use the count() function that is part of dplyr
count(coasters, Inversions)
```

Now that we have taken a look at the data, we are going to use this to construct a 90% confidence interval for the proportion of roller coasters with an inversion

```{r}
# perform a prop.test to take a look at the proportion of coasters with an inversion
prop.test(25, 57,p = NULL,
     conf.level = 0.9, correct = TRUE)
```
Based on this test, there is a 90% chance that the confidence interval of [0.328, 0.226] contains the true proportion of roller coasters with an inversion.

e. Now we are going to look at how much longer roller coasters with an inversion are compared to those without an inversion.

```{r}
# group the data by whether or not the coasters have inversions 
inversions <- coasters %>% filter(Inversions == "Yes")

no_inversions <- coasters %>% filter(Inversions == "No")

# Now I will use the data from this table to determine how much longer rollercoasters without an inversion are compared to those with one.
t.test(no_inversions$Length, inversions$Length)
```
To take a look at the difference in means, I used a two sample t test.  The results indicate that there is evidence to support a significant difference in the length of roller coasters with and without inversions. The average difference in lengths of coasters without inversions is between 900.24 and 2177.08 feet(p=1.206e-05, df = 52.535, 95% confidence). 
f. 
