---
title: "Exercise Set 3"
author: "Cora Ferguson"
date: "2/2/2023"
output: html_document
---

# Overview
The goal of this set of exercises is to practice some of the different things that we have been learning in class.  Some of these include importing data of different types, manipulating data, performing preliminary analyses, etc. 

## Question 1
a. The first task is to import the data into the file.  I set up my "Exercises" project in *RStudio* with version control through *GitHub* so I can access the notes and exercises even after I graduate.  With this in mind, my goal is to make the data easy to access so if anyone were to cone my repo, the would also be able to run this code sucessfully.  To do this, I will be using the `here()` function - I learned about this process in Biostats with Erika.

```{r}
# clear the environment window
rm(list = ls())

# import the appropriate libraries
library(readr)
library(here)

# import the data
dogs <- read_csv(here("Data", "dog_intelligence_clean.csv"))

# another way to do this without the here package:
# dogs <- read_csv("Data/ dog_intelligence_clean.csv")

```

b. The next task is to produce a `kable` table of the first 6 rows of the dogs data with a good caption. 

```{r}
# import the knitr package
library(knitr)

# use the kable function from the knitr package
knitr::kable(head(dogs[,1:5]),
             caption = "Data collected regarding canine intelligence from Stanley Coren at the University of British Columbia.")
```
c. The next task in question 1 is to creat a plot using `ggplot2`.  To do this, I will first import the `ggplot2` library and run the code provided in the exercise instructions. 

```{r fig.height=40}
# load the ggplot2 library
library(ggplot2)

# run the code
ggplot(dogs, aes(x = Breed, y = obey)) + geom_point() + coord_flip()

# using the gear icon, I increased the custom figure size to 40 to increase the height of the figure so it is not a squished
```

## Question 2
a. The first task is to create a vector storing a tuple

```{r}
# create a vector
x_vec <- c(0.167, 4.76, 370, 52, 82, 9492, 79)
```

b. Now I will extract the third number from this vector

```{r}
x_vec[3]
```
c. The next thing is to isolate the first 3 elements of this vector
```{r}
x_vec[1:3]
```

d. Now I will extract all of the elements of this vector except for the first element
```{r}
x_vec[-1]
```
## Question 3
a. Natural log

```{r}
log(x_vec[1])
```
b. Log base 10
```{r}
log(x_vec[2], base = 10)
```
c. Square root
```{r}
sqrt(x_vec[3])
```
d. Pi
```{r}
print(pi)
```
e. Exponential
```{r}
exp(x_vec)
```
f. Modulo
```{r}
# by dividing the different values inside of this vector by 2, it allows us to determine whether they are even or odd. 
x_vec%%2
```
g. Integer division
```{r}
x_vec[4] / 5
```
h. Determine the max and min value in a vector of numbers
```{r}
max(x_vec)

min(x_vec)
```
i. Determine the location of the max value in a vector
```{r}
# finding the location of the max
which(x_vec == max(x_vec), arr.ind = TRUE)
```

j. Determine the location of the min value in a vector
```{r}
# finding the location of the min
which(x_vec == min(x_vec), arr.ind = TRUE)
```
k. Represent the value of infinity
```{r}
Inf
```
## Question 4
a. The next task is to generate a tibble containing the data from a matrix on exam scores for three students. 
```{r}
library(tibble)

exam_scores <- data_frame(
     Exam1 = c(88, 75, 43),
     Exam2 = c(82, 81, 57),
     Exam3 = c(90, 85, 66),
     Exam4 = c(83, 78, 41)
)

exam_scores
```

## Question 5
Now, I will import the birthdays data. 





