---
title: "Exercise Set 6"
author: "Cora Ferguson"
date: "3/2/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The goal of exercise set 6 is to practice some of the `ggplot2` functions that we have been working with in class.  In this set of exercises, I will be using the "AmesHousing" dataset which encompasses housing data from Ames, IA.

First, I will set up the workspace and load the data into the environment:
```{r}
# clear environment
rm(list = ls())

# import the appropriate libraries
library(readr)
library(dplyr)
library(ggplot2)
library(here)

# import the dataset
AmesHousing <- read_csv(here("Data", "AmesHousing.csv"))
```
## Question 1
This series of exercises comes from the "06-data_visualization.Rmd" file that we have been working through. 

13) In the density plot above, explain what the `color`, `fill`, and `alpha` commands are used for. Hint: try running the code with and without these commands or use the Data Visualization Cheat Sheet. 

The `color` command is used to color the outline of a plot.  The `fill` command is used to fill the inside of a plot with a defined color.  The `alpha` command dictates the transparency of the plot with respect to the background. 

14) In the boxplot, what is done by the code `coord_flip()`?

In the boxplot, the `coord_flip` command causes the x and the y axis to switch.  This flips the boxplot from a vertical orientation to a horizontal orientation. 

15) Create a new boxplot, similar to the one above, but use `theme_bw()` instead of the given theme command. Explain how the graph changes.
```{r}
ggplot(AmesHousing, aes(x = Fireplaces, y = SalePrice, color = PavedDrive, group = PavedDrive)) +
  geom_boxplot() +
  labs(title="Housing Prices in Ames, Iowa") +
  theme(plot.title = element_text( color = "blue", face="bold", size=12, hjust=0))+
     theme_bw()
```
The background of the graph changes when I add in the `theme_bw()` command.  It causes the background to go from light grey to black and white. 


16) Use the tab completion feature in RStudio (type theme and hit the `Tab` key to see various options) to determine what theme is the default for most graphs in ggplot.
```{r}
theme_classic()
```
The classic theme is the default for most graphs in ggplot. This has a light grey background. 


17) In order to complete this activity, you will need to use the `dplyr` package to manipulate the dataset before making any graphics.
* Restrict the `AmesHousing` data to only sales under normal conditions. In other words, `Condition.1 == Norm`
* Create a new variable called `TotalSqFt = GRLivArea  +  TotalBsmtSF` and remove any homes with more than 3000 total square feet.
* Create a new variable, where `No` indicates no fireplaces in the home and `Yes` indicates at least one fireplace in the home.
* With this modified data file, create a graphic involving no more than three explanatory variables that best portrays how to predict sales price. For example, Figure 12 uses a linear model of kitchen quality, above ground square footage, and number of fireplaces to predict sale price.

```{r}
# cleaning up the AmesHousing data
AmesHousing_Clean <-
     AmesHousing %>%
     filter(Condition1 == "Norm") %>%
     mutate(TotalSqFt = GrLivArea  +  TotalBsmtSF) %>%
     filter(TotalSqFt < 3000) %>%
     mutate(Fireplaces_yn = case_when(Fireplaces <1 ~ 'No',
                           Fireplaces >= 1 ~ 'Yes',
                           ))
```

```{r}
# Creating a graphic that best predicts sale prices of houses
AmesHousing_Clean %>%
     ggplot(aes(x = YearBuilt, y= SalePrice)) +
     geom_point(aes(color = FullBath))+
     geom_smooth(method = lm)+
     facet_wrap(~Fireplaces_yn)+
     theme_bw()
```
For this graph, I am using the year built, the number of full bathrooms, and whether there is a fireplace or not to predict sale price. 

## Question 2
a. The first task is to reconstruct a plot using the `popmusic.csv` dataset.

```{r}
# import the data
popmusic <- read_csv(here("Data", "popmusic.csv"))
```
Here the x-axis is defined by the number of words, the y-axis is the ttr rating, and the plots are seperated by artist.
```{r}
popmusic %>%
     filter(artist == "Adele" | artist == "Beyonce" | artist == "Swift")%>%
     ggplot(aes(x=words, y = ttr))+
     geom_point()+
     geom_smooth(aes(color = artist))+
     facet_wrap(~artist)+
     theme(legend.position = "none")
```

b. The next task is to reconstruct a boxplot showing the spread of ttr data by artist.
```{r}
popmusic %>%
     ggplot(aes(x = artist, y = ttr))+
     geom_boxplot(aes(fill = artist))+
     scale_fill_brewer(palette = "Pastel2")+
     coord_flip()+
     labs(x = "Musical Artist", y = "Type-Tolkien Ratio", caption = "Comparing distributions of Type-Tolkien Ratios for six popular musical artists")+
     theme_bw()
     

```




