---
title: "Exercise Set 6"
author: "Cora Ferguson"
date: "3/2/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The goal of exercise set 6 is to practice some of the `ggplot2` functions that we have been working with in class.  In this set of exercises, I will be using the "AmesHousing" dataset which encompasses housing data from Ames, IA.

First, I will set up the workspace and load the data into the environment:
```{r}
# clear environment
rm(list = ls())

# import the appropriate libraries
library(readr)
library(dplyr)
library(ggplot2)
library(here)

# import the dataset
AmesHousing <- read_csv(here("Data", "AmesHousing.csv"))
```
## Question 1
This series of exercises comes from the "06-data_visualization.Rmd" file that we have been working through. 

13) In the density plot above, explain what the `color`, `fill`, and `alpha` commands are used for. Hint: try running the code with and without these commands or use the Data Visualization Cheat Sheet. 

The `color` command is used to color the outline of a plot.  The `fill` command is used to fill the inside of a plot with a defined color.  The `alpha` command dictates the transparency of the plot with respect to the background. 

14) In the boxplot, what is done by the code `coord_flip()`?

In the boxplot, the `coord_flip` command causes the x and the y axis to switch.  This flips the boxplot from a vertical orientation to a horizontal orientation. 

15) Create a new boxplot, similar to the one above, but use `theme_bw()` instead of the given theme command. Explain how the graph changes.

16) Use the tab completion feature in RStudio (type theme and hit the `Tab` key to see various options) to determine what theme is the default for most graphs in ggplot.

17) In order to complete this activity, you will need to use the `dplyr` package to manipulate the dataset before making any graphics.
