---
title: "Exercise Set 5"
author: "Cora Ferguson"
date: "2/23/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1 
The goal of this exercise set is to practice and become more familiar with `dplyr`. For this, I will be using a data set with metrics on song lyrics from popular artists. 

```{r}
# clear R's environment
rm(list = ls())
# import the libraries needed
library(dplyr)
library(readr)
library(here)

# import the data
popmusic <- read_csv(here("Data", "popmusic.csv"))
```
a. Create a new variable that counts the number of unique word in each song.
```{r}
popmusic <-
     popmusic %>%
     mutate(unique_words = ttr*words)

popmusic
```


b. Find the ten most sad/angry/downbeat songs. Keep only the artist and year in the resulting dataset.
```{r}
popmusic %>%
  select(artist, year, sentiment) %>%
     slice_max(sentiment, n = 10)
```

c. Find the number of songs from 2012 by either Bieber or Swift.
```{r}
popmusic %>%
  filter(year == "2012" & (artist == "Bieber"| artist == 
                             "Swift")) %>%
  group_by(artist)%>%
  summarise(n_songs = n())
  
```

d. Consider Adele only. Calculate the following all within the same chain of piped commands.

i. number of songs 
ii. median TTR, rounded to 2 decimal places.
proportion of songs with negative sentiment, rounded to 2 decimal places.
iii. highest (positive) sentiment
```{r}
popmusic %>%
  filter(artist == "Adele") %>%
  
  summarise(n_songs = n(),
            median_TTR = round(median(ttr), 2),
            neg_sentiment_prop = round((sentiment<0)/(sentiment),2),
            max_sentiment = max(sentiment)
            )
```

e. For each artist, determine the following. Again, try to structure your code so that it is a single chain of piped commands that begins with the full data set

i. number of songs
ii. number of albums
iii. the average sentiment for their songs
iv. average number of unique words per song
v. Then, sort the artists by their average level of positivity (with the most positive artist being first)
```{r}
popmusic %>%
  group_by(artist)%>%
  summarise(n_songs = n(),
            n_albums = n_distinct(year),
            avg_sentiment = mean(sentiment),
            avg_unique = mean(unique_words),
            avg_positive = mean(sentiment > 0)
            ) %>%
  arrange(desc(avg_positive))
```


## Question 2
Before I get to the questions, I am going to import the dataset

```{r}
library(ggplot2)

AmesHousing <- read_csv(here("Data", "AmesHousing.csv"))
```

1) In this dataset, how many houses were sold with four fireplaces?
```{r}
AmesHousing %>% 
     filter(Fireplaces == 4) %>%
     summarise(four_fireplaces = n())

# Create histogram for number of fireplaces
qplot(data=AmesHousing,x=Fireplaces)

```

2) What is the `facet` argument used for?
The `facet` argument is used to seperate different plots based on a specific variable that is different between the conditions. This can be used to group similar information together and/or split up other types of information based on different metrics.

3) Based upon the data documentation, what are the five different levels for kitchen quality?
The five different levels for kitchen quality are:
  Ex - excellent
  Gd - good
  TA - Typical/Average
  Fa - Fair
  Po - Poor

4) Do these graphs indicate that the quality of a kitchen could be related to the sale price?
These graphs do indicate that the quality of a kitchen could be related to the sale price. On average, as the sale price of the homes increases, so does the kitchen quality.

5) In the RStudio console, type `?qplot`. Modify the above code to create a barchart (`geom='bar'`) to count the number of sales for each level of kitchen quality. What is the difference between the color and fill command?
```{r}
# Create barchart for number of sales for each level of kitchen quality
qplot(data=AmesHousing,x=KitchenQual, geom = "bar")
```
The color command designates the color of the outline of the graph.  The fill command will dictate the color of the inside of the bars in the graph. 

6) Modify the code for histogram above so that the `aes` is not within the `geom`. However the resulting graph should look identical to the one above.
```{r}
# Create barchart for number of sales for each level of kitchen quality
qplot(data=AmesHousing,x=KitchenQual)
```

7) Create a scatterplot using `ggplot` with **Fireplaces** as the x-axis and **SalePrice** as the y-axis.
```{r}
# create a scatterplot comparing fireplaces to sale price

ggplot(data = AmesHousing)+
  geom_point(mapping = aes(Fireplaces, SalePrice))
```


8) Create a histogram of the above ground living area, `GrLivArea`.
```{r}
ggplot(data = AmesHousing)+
  geom_histogram(mapping = aes(GrLivArea))
```


9) Create a scatterplot using `Year.Built` as the explanatory variable and `SalePrice` as the response variable. Include a regression line, a title, and labels for the x and y axes.
```{r}
# create scatterplot comparing year built to sale price
ggplot(data = AmesHousing) +
  geom_point(mapping = aes(x=YearBuilt, y = SalePrice))+
  geom_smooth(mapping = aes(x=YearBuilt, y=SalePrice), method = lm)+
  labs(title= "Figure 1: Sale prices in Ames, IA based on the year houses were built", x= "Year Homes were Built", y="Sale Price of individual homes")
  
```

10) Modify the scatterplot in Question 9) so that there is still only one regression line, but the points are colored by the overall condition of the home, `Overall.Cond`. 
```{r}
# create scatterplot comparing year built to sale price
ggplot(data = AmesHousing) +
  geom_point(mapping = aes(x=YearBuilt, y = SalePrice, color = OverallCond))+
  geom_smooth(mapping = aes(x=YearBuilt, y=SalePrice, color = OverallCond), method = lm)+
  labs(title= "Figure 1: Sale prices in Ames, IA based on the year houses were built", x= "Year Homes were Built", y="Sale Price of individual homes")
  
```
