---
title: "STAT/DATA 234 - Quiz 2"
output: html_notebook
---

## Question 1
The first think that I will do is import the libraries that I will need and load the *starwars* data that is available in the `dplyr` package.
```{r}
# import libraries
library(dplyr)

# import dataset
data("starwars")
```

## Question 2
Now I will construct a dataset containing only the humans and droids.
```{r}
starwarsHD <- starwars %>%
     filter(species=="Human" | 
            species =="Droid")

starwarsHD
```
## Question 3
Using the *starwarsHD* tibble, I will calculate the BMI for each individual and store it as a new object. In this dataset, the height of the characters is listed in cm and the mass is listed in kg.  To accomodate for that, I must use the metric BMI calculation which is as follows: 

BMI = (Weight in Kilograms / (Height in Meters x Height in Meters))
```{r}
# since the height is in cm, we need to multiply it by 0.01 to convert it into meters
starwarsBMI <- starwarsHD %>%
     mutate(BMI = mass/((height*0.01)*(height*0.01)))

starwarsBMI
```
## Question 4
The next task is to consruct another tibble that only keeps the name, species and BMI of the characters.  I will also sort this in a way that places the characters with the highest BMI at the top.
```{r}
starwarsBMI %>%
     select(name, species, BMI) %>%
     arrange(desc(BMI))
```
## Question 5
The last task is to calculate the total number of characters and the average BMI for both the humans and the droids.
```{r}
starwarsBMI %>%
     group_by(species) %>%
          summarise(n_characters = n(),
                    avg_BMI = mean(BMI, na.rm=TRUE))
```



