---
title: "Project 3"
author: "Cora Ferguson"
date: "3/5/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project 3

### Overview
The goal of this project is to practice dealing with data scraped using a shiny app developed at St. Lawrence University on the TV show *Modern Family*.  

```{r}
rm(list = ls())
# load in the libraries we will need
library(here)
library(dplyr)
library(ggplot2)
library(readr)

# load the data
TV <- read_csv(here("Data", "imdb_data.csv"))

```
### Required Analyses

1. Display the IMDb ratings by season
```{r}
TV <- TV %>%
        mutate(seasonNumber_fct = factor(seasonNumber))

IMDb_by_season <- 
        TV %>%
     ggplot(aes(x = seasonNumber_fct, y = averageRating)) +
     geom_boxplot(aes(color = seasonNumber_fct))+
     labs(x = "Season", y = "IMBd Ratings", color = "Season\nNumber", caption = "Fig. 1: IMBd rating data for the episodes of Modern Family seperated by season.")+
     theme_bw()+
        theme(legend.position="none")
        

IMDb_by_season

ggsave("IMDb_by_season.png", width = 6, height = 4)
```
```{r}
TV %>%
        group_by(seasonNumber) %>%
        summarise(meanrating = mean(averageRating),
                  greatestEpisode = max(averageRating))

TV %>%
        slice_max(averageRating, n=1) 

TV %>%
slice_min(averageRating,n=1)
```


2. Display the trend in IMDb rating as the series progresses (i.e., using Overall Episode Number)
```{r}
IMBD_trend <-
TV %>%
     ggplot(aes(x = episodeNumber_overall, y = averageRating)) +
     geom_point(aes(color = seasonNumber_fct))+
     labs(x = "Overall Episode Number", y = "Average Rating", color = "Season\nNumber", caption = "Fig. 2: Average IMDb rating for each episode produced.")+
        theme_bw()+
        geom_smooth(method = lm)
        

IMBD_trend



ggsave(filename = "IMBD_trend.png", 
       plot = IMBD_trend,
       width = 6, 
       height = 4)
        
```
```{r}
IMBD_trend2 <-
TV %>%
     ggplot(aes(x = episodeNumber_overall, y = averageRating)) +
     geom_point(aes(color = seasonNumber_fct))+
     labs(x = "Overall Episode Number", y = "Average Rating", color = "Season\nNumber", caption = "Fig. 3: Average IMDb rating for each episode produced.")+
        theme_bw()+
        geom_smooth(method = lm)+
        coord_cartesian(ylim = c(0,10))

IMBD_trend2



ggsave(filename = "IMBD_trend2.png", 
       plot = IMBD_trend2,
       width = 6, 
       height = 4)
        
```

3. Analyzing Season Finales (i.e., the last episode in each season)
```{r}
# convert season number to factor
TV <- TV %>% 
        mutate(seasonNumber = factor(seasonNumber))

# pick out the last episode of each season
TV_Finale <- TV %>%
        group_by(seasonNumber) %>%
        slice_max(episodeNumber_in_season, n=1)

TV_Finale
```

This can be using either a table or graph. Choose whichever you think you can display better.
```{r}
# re order the episode names by the season number
library(forcats)
# creating a graph for the ratings of the season finales
IMBD_finale <-
TV_Finale %>%
        ggplot(aes(x = seasonNumber, y = averageRating, color = numVotes))+
        geom_point(size = 3)+
     labs(x = "Season Number", y = "Average Rating", color = "Number of Votes", caption = "Fig. 4: Average IMBd ratings for each season finale and the number of votes\nthey recieved.")+
        theme_bw()

IMBD_finale

ggsave(filename = "IMBD_finale.png", 
       plot = IMBD_finale,
       width = 6, 
       height = 4)
```

