---
title: "Project 3"
author: "Cora Ferguson"
date: "3/5/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project 3

### Overview
The goal of this project is to practice dealing with data scraped using a shiny app developed at St. Lawrence University on the TV show *Modern Family*.  

```{r}
# load in the libraries we will need
library(here)
library(dplyr)
library(ggplot2)
library(readr)

# load the data
TV <- read_csv(here("Data", "imdb_data.csv"))

```
### Required Analyses

1. Display the IMDb ratings by season
```{r}
TV %>%
     ggplot(aes(x = seasonNumber, y = averageRating)) +
     geom_point()+
     labs(x = "Season Number", y = "Average Rating")
```
2. Display the trend in IMDb rating as the series progresses (i.e., using Overall Episode Number)
```{r}
TV %>%
     ggplot(aes(x = episodeNumber_overall, y = averageRating)) +
     geom_point()+
     labs(x = "Overall Episode Number", y = "Average Rating")
```

3. Analyzing Season Finales (i.e., the last episode in each season)
```{r}
# convert season number to factor


# pick out the last episode of each season
TV_Finale <- TV %>%
     group_by(seasonNumber) %>%
     slice_max(~episodeNumber_in_season, n=1)
```

This can be using either a table or graph. Choose whichever you think you can display better.

